|

### 2025-01-22 doc/paper.qmd
Added structured subsections

## Research Design Choices and Assumptions - Task 1 {#sec-research_design_assumptions1}
The aim of Assignment I is to replicate a specific empirical figure (Figure 3) from the report by @EC_Report_2024. This figure involves analyzing the market shares of audit firms (Big 4, CR4, and 10KAP) across EU countries and at the EU level for PIE statutory audits conducted in 2021. The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures. For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

@@

## Replication Steps - Task 1 {#sec-replication_steps1}

@@

## Results - Task 1 {#sec-results}
To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`. The analysis of market shares for statutory audits across European countries reveals distinct patterns of market concentration and auditor dominance. Big 4 firms exhibit a significant presence, often commanding a dominant share in many countries. For example, countries such as the Czech Republic, Estonia, and Finland demonstrate Big 4 market shares exceeding 95%, reflecting the significant influence of these firms in specific markets. However, the extent of this dominance varies, with lower Big 4 shares observed in countries like Bulgaria (17.5%) and Greece (43.6%), indicating a more diversified audit market in these regions. The analysis reveals that the Big 4 hold a market share exceeding 80% in 11 EU countries. This aligns with rthe finding of @EC_Report_2024, which similarly highlights that the Big 4 dominate over 80% of the market share in 11 Member States.

@@

# Task 2 - Extending the Analysis to 2007–2023 {#sec-task2}

# Task 3 - Cross-Country Replication {#sec-task3}

>>>>

## Research Design Choices and Assumptions {#sec-research_design_assumptions1}
The aim of Assignment I is to replicate a specific empirical figure (Figure 3) from the report by @EC_Report_2024. This figure involves analyzing the market shares of audit firms (Big 4, CR4, and 10KAP) across EU countries and at the EU level for PIE statutory audits conducted in 2021. The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures. For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

@@

## Replication Steps {#sec-replication_steps1}

@@

## Results {#sec-results1}
To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`. The analysis of market shares for statutory audits across European countries reveals distinct patterns of market concentration and auditor dominance. Big 4 firms exhibit a significant presence, often commanding a dominant share in many countries. For example, countries such as the Czech Republic, Estonia, and Finland demonstrate Big 4 market shares exceeding 95%, reflecting the significant influence of these firms in specific markets. However, the extent of this dominance varies, with lower Big 4 shares observed in countries like Bulgaria (17.5%) and Greece (43.6%), indicating a more diversified audit market in these regions. The analysis reveals that the Big 4 hold a market share exceeding 80% in 11 EU countries. This aligns with rthe finding of @EC_Report_2024, which similarly highlights that the Big 4 dominate over 80% of the market share in 11 Member States.

@@

# Task 2 - Extending the Analysis to 2007–2023 {#sec-task2}
## Research Design Choices and Assumptions {#sec-research_design_assumptions2}
## Replication Steps {#sec-replication_steps2}
## Results {#sec-results2}

# Task 3 - Cross-Country Replication {#sec-task3}
## Research Design Choices and Assumptions {#sec-research_design_assumptions3}
## Replication Steps {#sec-replication_steps3}
## Results {#sec-results3}
